Calculating Entropies With Nested Sampling

### 2017-01-15 paper/ms.tex
Mutual information formula
More on mutual information

In a standard situation where Bayesian inference would be used,
the unknown quantities are the parameters $\x$ and the data $\d$
(which subsequently becomes known). The prior information leads the
user to specify a prior distribution $p(\x)$ for the unknown parameters,
along with a ``sampling distribution'' $p(\d | \x)$ describing prior knowledge
of how the data is related to the parameters. By the product rule, this yields
a joint prior
\begin{align}
p(\x, \d) &= p(\x)p(\d | \x)
\end{align}

@@

\subsection{Mutual information}

The mutual information is
\begin{align}
I_{\x, \d} &= \sum_{\x} \sum_{\d}
\end{align}

>>>>

In a standard situation where Bayesian inference would be used,
the unknown quantities are the parameters $\x$ and the data $\d$
(which subsequently becomes known). The prior information leads the
user to specify a prior distribution $p(\x)$ for the unknown parameters,
along with a ``sampling distribution'' $p(\d | \x)$ describing prior knowledge
of how the data is related to the parameters. By the product rule, this yields
a {\em joint prior}
\begin{align}
p(\x, \d) &= p(\x)p(\d | \x)
\end{align}

The entropy of this joint prior describes the degree to which the question
``what is the value of the pair $(\x, \d)$?'' remains unanswered.

@@

\subsection{Mutual information}
The mutual information is another way of describing the relevance of the
data to the parameters.

Its definition is
\begin{align}
I_{\x, \d} &= \sum_{\x} \sum_{\d} p(\x, \d)
                       \log\left[\frac{p(\x, \d)}{p(\x)p(\d)}\right]\\
           &= H_{\x} + H_{\d} - H_{\x, \d}.
\end{align}
For present purposes, it is more conveniently written as
\begin{align}
I_{\x, \d} &= \sum_{\x} \sum_{\d} p(\x, \d)
              \log\left[\frac{p(\d | \x)}{p(\d)}\right].
\end{align}
As with the conditional entropy, we see that the difficulty appears in the
form of the log of the marginal likelihood,
$\log p(\d) = \log \sum_{\x} p(\x)p(\d | \x)$.

For experimental design purposes, maximising either $I_{\x, \d}$ or
$H_{\x | \d}$ will produce the same result. {\todo Mention reference priors?}
